Viscous Erosion in Porous Media

### 2018-01-18 docs/methods/erosion_methods.tex
Working on paper.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.85 \textwidth]{./figs/01bodseq.pdf}
\caption{A single body eroding in Stokes flow. As the body erodes, it develops a corner at its front and rear stagnation points, while remaining for-aft symmetric due to time-reversibility. Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress. In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
\label{01bodseq}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.80 \textwidth]{./figs/shrink_intface.pdf}
\caption{Shape and stress evolution. (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals. Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes. (b) The distribution of absolute shear stress, $\atau$, along each of the interfaces. Initially the stress is distributed non-uniformly, but becomes more uniform 
}
\label{shrink_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

@@

\vsp{5}
Later, as a segue to discuss the vanishing of area, I can point out that the interface spacing becomes greater at later times in Fig. 5a.

\subsubsection{Shape evolution}

In Fig.~5a, we visualize the interfaces color coded in time. In Fig.~5b,
we show the absolute shear stress, $\atau$, as it varies over the
surface of the body. Initially, the shear stress is a hump shape. As
time progresses, the stress becomes more evenly distributed, with the
exception of the front/rear corner where the curvature is high.

@@

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.80 \textwidth]{./figs/01bodseq.pdf}
\caption{A single body eroding in Stokes flow. As the body erodes, it develops a corner at its front and rear stagnation points, while remaining for-aft symmetric due to time-reversibility. Color indicates the vorticity of the surrounding flow, which, when evaluated on the boundary, gives the local shear stress. In this simulation, we use $N_\iin = 1024$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt = 1E-6$, and smoothing parameters of $\eps = 10/1024$ and $\sigma = 10/1024$.}
\label{01bodseq}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

@@

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.75 \textwidth]{./figs/shrink_intface.pdf}
\caption{Shape and stress evolution. (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals. Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes. (b) The distribution of absolute shear stress, $\atau$, along each of these interfaces. Normalized arc length, $s/L$, runs counterclockwise from the rear stagnation point. The stress initially varies over the body's surface, but becomes more uniform over time.
}
\label{shrink_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

\subsection{Scaling law for the vanishing rate}

Interestingly, a brief look at Fig.~\ref{shrink_intface}(a) reveals that the spacing between successive interfaces becomes larger as the body shrinks, suggesting that the overall shear stress is growing. Of course, such a relationship is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu V / L$, since stress is inversely proportional to body size. In two dimensions, though, this law is modified. The correct modification can be inferred

Interestingly, the spacing between successive interfaces in Fig.~\ref{shrink_intface}(a) becomes larger as time progresses

\subsection{The limiting shape}

\vsp{30}
Later, as a segue to discuss the vanishing of area, I can point out that the interface spacing becomes greater at later times in Fig. 5a.

@@

In the table, we measure the error in the shape by computing the L2-difference of the interfaces.
